The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2025-10-24 SIGMA/SIGMA_submission/borel_reg_submission.tex
Moved acknowledge section before references (as required) and thanks referees

Sometimes, in expressions like
\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\;d\zeta(a')\,, \]
it is useful to give a name $a'$ to the point moving along the integration path. In this case, all of the functions and differential forms whose values change along the integration path are explicitly evaluated at $a'$.    
\end{notation*}
%
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
%
\section{Historical context}\label{sec:historical-context}
%
\subsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $\Phi$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).

@@

Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries} we get 
\begin{equation*}
\begin{split}
\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
\end{split}
\end{equation*}
We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence. This ends the proof of part~\ref{part-2-prf}.

@@

Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;f = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi. \]
Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
\[ f = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi, \]
which rearranges to the second equation in the statement.
\end{proof}
\newpage
\bibliographystyle{utphys}
%\bibliographystyle{plain}
\bibliography{biblio_borel_reg}
\end{document}

>>>>

Sometimes, in expressions like
\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\;d\zeta(a')\,, \]
it is useful to give a name $a'$ to the point moving along the integration path. In this case, all of the functions and differential forms whose values change along the integration path are explicitly evaluated at $a'$.    
\end{notation*}
%
\section{Historical context}\label{sec:historical-context}
%
\subsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $\Phi$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).

@@

Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries}~we~get 
\begin{equation*}
\begin{split}
\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
\end{split}
\end{equation*}
We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence. This ends the proof of part~\ref{part-2-prf}.

@@

Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;f = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi. \]
Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
\[ f = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi, \]
which rearranges to the second equation in the statement.
\end{proof}

\subsection*{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions. We would like to thank the anonymous referees for many helpful suggestions.

\bibliographystyle{sigma}
%\bibliographystyle{plain}
\bibliography{biblio_borel_reg}
\end{document}
